Block bootstrap consistency\\under weak assumptions

### 2016-05-23 Paper.tex
[#21] remove duplicated VERSION.tex input
The LaTeX file loaded VERSION.tex a second time, after some code that
checks whether the file exists and loads it if it does. This
duplication was either (1) unnecessary, if the file exists, or (2)
causes an error, if the file doesn't.

This commit closes #21.
[#24] Add AucTeX variables to LaTeX files
This will make life slightly easier. The commit closes #24
[#23] Fix incorrect equation reference in Proof of Lemma 3
Closes #23.

\documentclass[11pt]{article}
\IfFileExists{VERSION.tex}{\input{VERSION}}%
{\date{Pdf compiled \today. (Version unclear; run `make VERSION.tex'.)}}
\input{preamble}
\input{VERSION}
\begin{document}

@@

\begin{proof}
  For~\eqref{eq:26}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
  M_{nj})$ is a uniformly integrable martingale difference array, by
  Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}, and
  satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
  For~\eqref{eq:26}, observe that
  \begin{equation*}
    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big| \leq
    2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
    \Big(\tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2\Big)^{1/2}
    + \tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2
  \end{equation*}
  after several applications of the Cauchy-Schwarz
  inequality. Lemma~\ref{lln-for-real-zsq}, along with~\eqref{eq:17}
  and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
  $(1/n) \sum_t (\mu_{nt} - \bar X)^2$ converges to zero in
  probability by assumption on $\mu_{nt} - \bar\mu_n$ and because
  $\bar X$ itself obeys the \lln.

@@

>>>>

\documentclass[11pt]{article}
\IfFileExists{VERSION.tex}{\input{VERSION}}%
{\date{Pdf compiled \today. (Version unclear; run `make VERSION.tex'.)}}
\input{preamble}
\begin{document}

@@

\begin{proof}
  For~\eqref{eq:25}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
  M_{nj})$ is a uniformly integrable martingale difference array, by
  Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}, and
  satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
  For~\eqref{eq:26}, observe that
  \begin{equation*}
    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big| \leq
    2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
    \Big(\tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2\Big)^{1/2}
    + \tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2
  \end{equation*}
  after several applications of the Cauchy-Schwarz
  inequality. Lemma~\ref{lln-for-real-zsq}, along with~\eqref{eq:17}
  and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
  $(1/n) \sum_t (\mu_{nt} - \bar X)^2$ converges to zero in
  probability by assumption on $\mu_{nt} - \bar\mu_n$ and because
  $\bar X$ itself obeys the \lln.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
